An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-02-16 EconGrowth.Rnw
Now trying nlxb for CES.

  }
  # Runs a non-linear least squares fit to the data with constraints
#   modelCES <- nls(iGDP ~ ((1-gamma_E)^(1.0/sigma) * ((exp(lambda_L*iYear))^beta 
#                                                   * iLabor^beta
#                                                   * iCapStk^(1-beta) )^((sigma-1.0)/sigma) 
#                           + gamma_E^(1.0/sigma)*(exp(lambda_E*iYear) 
#                                                   * iEToFit)^((sigma-1.0)/sigma))^(sigma/(sigma-1.0)), 
#                   data=dataTable,
#                   start=list(sigma=sigmaGuess, gamma_E=gamma_EGuess, beta=betaGuess, 
#                              lambda_L=lambda_LGuess, lambda_E=lambda_EGuess),
#                   control=nls.control(maxiter=10000, tol=1e-05, minFactor=1/1024, 
#                                       printEval=TRUE, warnOnly=TRUE),
#                   algorithm = "port",
#                   lower = lower,
#                   upper = upper
#                   )
  model <- iGDP ~ ((1-gamma_E)^(1.0/sigma) * ((exp(lambda_L*iYear))^beta 
                                                  * iLabor^beta
                                                  * iCapStk^(1-beta) )^((sigma-1.0)/sigma) 
                          + gamma_E^(1.0/sigma)*(exp(lambda_E*iYear) 
                                                  * iEToFit)^((sigma-1.0)/sigma))^(sigma/(sigma-1.0))
  modelCES <- nlxb(model,
                   data=dataTable,
                   start=list(sigma=sigmaGuess, gamma_E=gamma_EGuess, beta=betaGuess, 
                              lambda_L=lambda_LGuess, lambda_E=lambda_EGuess)
                   )
print(class(modelCES))
print(modelCES)
  modelCES <- wrapnls(modelCES)
print(class(modelCES))
  return(modelCES)
}
print("US Q")
print(summary(cesModel("US", "Q")))

>>>>

  }
  # Runs a non-linear least squares fit to the data with constraints
#   modelCES <- nls(iGDP ~ ((1-gamma_E)^(1.0/sigma) * ((exp(lambda_L*iYear))^beta 
#                                                   * iLabor^beta
#                                                   * iCapStk^(1-beta) )^((sigma-1.0)/sigma) 
#                           + gamma_E^(1.0/sigma)*(exp(lambda_E*iYear) 
#                                                   * iEToFit)^((sigma-1.0)/sigma))^(sigma/(sigma-1.0)), 
#                   data=dataTable,
#                   start=list(sigma=sigmaGuess, gamma_E=gamma_EGuess, beta=betaGuess, 
#                              lambda_L=lambda_LGuess, lambda_E=lambda_EGuess),
#                   control=nls.control(maxiter=10000, tol=1e-05, minFactor=1/1024, 
#                                       printEval=TRUE, warnOnly=TRUE),
#                   algorithm = "port",
#                   lower = lower,
#                   upper = upper
#                   )
  model <- iGDP ~ ((1-gamma_E)^(1.0/sigma) * ((exp(lambda_L*iYear))^beta 
                                                  * iLabor^beta
                                                  * iCapStk^(1-beta) )^((sigma-1.0)/sigma) 
                          + gamma_E^(1.0/sigma)*(exp(lambda_E*iYear) 
                                                  * iEToFit)^((sigma-1.0)/sigma))^(sigma/(sigma-1.0))
  modelCES <- nlxb(model,
                   data=dataTable,
                   start=list(sigma=sigmaGuess, gamma_E=gamma_EGuess, beta=betaGuess, 
                              lambda_L=lambda_LGuess, lambda_E=lambda_EGuess)
                   )
print(modelCES)
  return(modelCES)
}
print("US Q")
print(summary(cesModel("US", "Q")))
